RNA-seq Analysis

### 2021-04-15 inst/analysis/rnaseq.Rmd
format rnaseq analysis report

```{r}
withr::with_dir(here::here(), {
  rnaseq_pca <- tar_read(rnaseq_pca)
  rnaseq_different_differences <- tar_read(rnaseq_different_differences)
})
```

@@

```{r}
rnaseq_pca
```

@@

```{r}
head(rnaseq_different_differences, 20)
```

>>>>

```{r}
withr::with_dir(here::here(), {
  pca <- tar_read(rnaseq_pca)
  deg <- tar_read(rnaseq_different_differences)
  gsea_p <- tar_read(rnaseq_gsea_plot)
  tfea_p <- tar_read(rnaseq_tfea_plot)
})
```

@@

```{r}
pca
```

@@

```{r}
deg %>% 
  dplyr::select(row, symbol, description, lg2fc = log2FoldChange, padj) %>% 
  head(20) %>% 
  my_kable()
```

## Gene Set Enrichment Analysis

```{r}
gsea_p
```

## Transcription Factor Analysis

```{r}
tfea_p
```
